Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-18 WRITEUP/ms.tex
typeset edits

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the images are resolved
but not within the multiply lensed emission (i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a};see \citealt{Bussmann15a} for details of
the code). Model of each slice in \Fig{model} thus provides
properties on the intrinsic kinematics. The slices
are obtained by binning the data (over the full linewidth
$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
 to increase the SNR.

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
larger than the astrometry uncertainties in the VLA image and is
constrained by the uncertainties provided from previous SIE lens model (C06).
We initialize the Einstein Radius based on the optical SIE lens
model by C06 and impose a uniform prior using their reported $\pm$3$\sigma$.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

@@

We first obtain a preliminary lens model for each channel slice independently,
where their lens parameters are allowed to vary and are initialized according
to the aforementioned way. We obtain the final model
by repeating the modeling over each slice but fixing their lens parameters
according to the overall median in the preliminary models, as listed in \Tab{lens}. The corresponding masses within the Einstein radii is
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun.
This ensures that all models share the same lens profile.
The magnification factor is determined by taking the ratio
between the image plane flux of the model and the source plane flux.
The best-fit magnification factors are listed in \Tab{model}.
We compare our model parameters in \Tab{lens} describing
the mass distribution of the lensing galaxy
against that of the SIE model presented by C06. The position
%\footnote{We note that they report a positional offset
% relative to the light centroid in the HST image, which are at slightly
%different astrometry. Our comparison takes into
%account the astrometric correction applied.}
of lensing mass, Einstein Radius, PA and axial ratio
are all consistent within the uncertainties.
% PA = -73.6, ellipticity = 0.45,
% their theta\_R = 1.84" $\pm$ 0.01.

\subsection{Interpretation and Caveats}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient in the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the observed (image plane) velocity field and
the double-horned line profile in \Fig{CO21spec}. Furthermore,
the reconstructed source plane emission in optical-NIR
is also best-reproduced using a $n$\,=\,1 Sersic profile (C06).
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

% the companion
One interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
separated by $\sim$2.4\,kpc away from the AGN host galaxy.

We emphasis that the spatial resolution of the data at hand
is a few arcsec, which implies that despite the high SNR and spectral
resolution, this data is insufficient to constrain the
intrinsic sizes of the lensed galaxies, and thus the magnification
factors is likely under-predicted. We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
channel slice $\sim$100\,\kms of the \bco data. Top: Channel maps of the
PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
The location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line. The locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses (see text in \Sec{lensmodel} for caveats).
The caustic curves are represented as cyan lines. The beam of the
PdBI observations is shown in the bottom right corner of each panel.
Bottom: Residual images of the best-fit models, obtained by
taking the Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain. Contours start
at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
\label{fig:model}}
\end{figure*}

@@

The highly asymmetric \bco line profile also suggests that differential lensing is non-negligible in the CO emission, where
flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{mag}.
\input{table_magFactor}

>>>>

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel} %DONE
At the angular resolution of the \bco data, the images are resolved
but not within the multiply lensed emission (i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Model of each slice in \Fig{model} thus provides
properties on the intrinsic kinematics. The slices
are obtained by binning the data (over the full linewidth
$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
 to increase the SNR.

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06 
and impose a uniform prior using $\pm$3$\sigma$ from their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

@@

We first obtain a preliminary lens model for each channel slice independently,
where their lens parameters are allowed to vary and are initialized according
to the aforementioned way. We obtain the final model
by repeating the modeling over each slice but fixing their lens parameters
according to the overall median in the preliminary models, as listed in \Tab{lens}. 
This ensures that all models share the same lens profile.
The magnification factor is determined by taking the ratio
between the image plane flux of the model and the source plane flux.
The best-fit magnification factors are listed in \Tab{model}.

Our model parameters in \Tab{lens}, describing
the mass distribution of the lensing galaxy, are consistent (within the uncertainties) 
with that of the SIE model presented by C06. We find a mass of 
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
within the Einstein radius.

\input{table_medianLens}

\subsubsection{Interpretation and Caveats} \label{sec:caveat}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient in the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
$\sim$2.4\,kpc away from the AGN host galaxy.

We emphasize that the spatial resolution of the data at hand
is a few arcsec, which implies that despite the high SNR and spectral
resolution, this data is insufficient to constrain the
intrinsic sizes of the lensed galaxies, and thus the magnification
factors ares likely under-predicted. 
We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
channel slice $\sim$100\,\kms of the \bco data. Top: channel maps of the
PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
The location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line. The locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses (see text in \Sec{caveat} for caveats).
The caustic curves are represented as cyan lines. The beam of the
PdBI observations is shown in the bottom right corner of each panel.
Bottom: residual images of the best-fit models, obtained by
taking the Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain. Contours start
at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
\label{fig:model}}
\end{figure*}

@@

The highly asymmetric \bco line profile also suggests that differential lensing is non-negligible in the CO emission, where
flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{model}.
\input{table_magFactor}

### 2016-05-18 WRITEUP/table_medianLens.tex
typeset edits

\begin{deluxetable*}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Lens parameters from preliminary models}
\tablehead{
\multicolumn{2}{c}{Parameters} &
\colhead{Median values} % weighted-mean of median of each
}
\startdata
Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
Axial Ratio      &             & 0.56$\pm$0.16\\
Position Angle   & (deg)       & 103$\pm$22\\
Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002\\
\enddata
\label{tab:lens}
\tablecomments{ Parameters describing the foreground lens are
obtained based on the preliminary models (see text for details).
All angular offsets are with respect to
$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
$\delta$\,=\,-12\degr31\arcmin58\farcs3 (J2000).
The corresponding masses
within the Einstein radii is $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\,\Msun.}
\end{deluxetable*}

>>>>

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Lens parameters from preliminary models}
\tablehead{
\multicolumn{2}{c}{Parameters} &
\colhead{Median values} % weighted-mean of median of each
}
\startdata
Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
Axial Ratio      &             & 0.56$\pm$0.16\\
Position Angle   & (deg)       & 103$\pm$22\\
Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002
\enddata
\label{tab:lens}
\tablecomments{Parameters describing the foreground lens are
obtained based on the preliminary models (see text for details).
All angular offsets are with respect to
$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
$\delta$\,=\,-12\degr31\arcmin58\farcs3 (J2000).}
\end{deluxetable}
